Gaia's constraints on the extremely massive ($\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-11 VFTS682_APJL.tex
new fig and angle data: TO BE CHECKED

      \multicolumn{5}{l}{\emph{Gaia's relative proper motion for VFTS
      682 }} \\
      \hline
      &$\delta\mu_\mathrm{RA}$  &[$\masyr$] & $0.103\pm0.080$ & (1,4) \\
      &$\delta\mu_\mathrm{DEC}$  &[$\masyr$] & $0.086\pm0.100$ &  (1,4) \\
      &$\delta\mu_\mathrm{}$  &[$\masyr$] & $0.13\pm0.09$ &  (1,4) \\
                 &$v_\mathrm{2d}$  &[$\kms$] & $32\pm21$ & (1,4)\\  
                     &$\theta$  &[degrees] &  \SdM{$14.2_{-xx}^{+xx}$}  & (1,4)\\  
                         &$v_\mathrm{2d, \parallel}$  &[$\kms$] & $\SdM{xxx}\pm\SdM{xxx}$ & (1,4)\\  
 %

 \hline     
          \multicolumn{5}{l}{\emph{HST's relative proper motion for VFTS 682}} \\
            \hline
      &$\delta\mu_\mathrm{RA, HST}$  &[$\masyr$] & $0.01\pm0.13$ & (3) \\
      &$\delta\mu_\mathrm{DEC, HST}$  &[$\masyr$] & $0.20\pm0.10$ &  (3) \\
       &$\delta\mu_\mathrm{HST}$  &[$\masyr$] & $0.20\pm0.10$ &  (3) \\
                  &$v_\mathrm{2d, HST}$  &[$\kms$] & $47\pm24$ & (3)\\  
                      &$\theta^{*}$  &[degrees] &   \SdM{$xx_{-xx}^{+xx}$}   & (1,4)\\  
                          &$v_\mathrm{2d, \parallel}$  &[$\kms$] & $\SdM{xxx}\pm\SdM{xxx}$ & (1,4)\\  
 %

@@

\begin{figure*}[htbp]
  \centering
  \includegraphics[width=0.35\textwidth]{figures/dist_mu_region.pdf}
  \includegraphics[width=0.35\textwidth]{figures/angle}
  \caption{Left panel: distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136. VFTS682 is not an outlier, but
    its relative proper motion matches the expected value if it were indeed
    ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. The top axis shows the conversion to physical units
    assuming a distance of 50\,kpc. Right panel:  distribution of
    angles between the relative proper motion direction and the radial
    direction to the star. The error bars for VFTS682 are large, but
    the best value is in agreement with the hypothesis of dynamical
    ejection. In both
    panels, the dark blue histograms contain 317 
    stars with error smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
    lighter blue histograms contain 36 stars with errors smaller than $0.05\,\mathrm{mas \
      yr^{-1}}$. \SdM{ Todo: [1] insert correct errorbars in right pabel}}
  \label{fig:mu_dist}
\end{figure*}

>>>>

      \multicolumn{5}{l}{\emph{Gaia's relative proper motion for VFTS
      682 }} \\
      \hline
      &$\delta\mu_\mathrm{RA}$  &[$\masyr$] & $0.103\pm0.080$ & (1,4) \\
      &$\delta\mu_\mathrm{DEC}$  &[$\masyr$] & $0.086\pm0.100$ &  (1,4) \\
      &$\delta\mu_\mathrm{}$  &[$\masyr$] & $0.13\pm0.09$ &  (1,4) \\
                 &$v_\mathrm{2d}$  &[$\kms$] & $32\pm21$ & (1,4)\\  
                     &$\theta$  &[degrees] &  $14.2_{-43}^{+44}$  & (1,4)\\  
                         &$v_\mathrm{2d, \parallel}$  &[$\kms$] & $\SdM{xxx}\pm\SdM{xxx}$ & (1,4)\\  
 %

 \hline     
          \multicolumn{5}{l}{\emph{HST's relative proper motion for VFTS 682}} \\
            \hline
      &$\delta\mu_\mathrm{RA, HST}$  &[$\masyr$] & $0.01\pm0.13$ & (3) \\
      &$\delta\mu_\mathrm{DEC, HST}$  &[$\masyr$] & $0.20\pm0.10$ &  (3) \\
       &$\delta\mu_\mathrm{HST}$  &[$\masyr$] & $0.20\pm0.10$ &  (3) \\
                  &$v_\mathrm{2d, HST}$  &[$\kms$] & $47\pm24$ & (3)\\  
                      &$\theta^{*}$  &[degrees] &   $-35_{-51}^{+24}$   & (1,4)\\  
                          &$v_\mathrm{2d, \parallel}$  &[$\kms$] & $\SdM{xxx}\pm\SdM{xxx}$ & (1,4)\\  
 %

@@

\begin{figure*}[htbp]
  \centering
  \includegraphics[width=0.35\textwidth]{figures/dist_mu_region.pdf}
  \includegraphics[width=0.35\textwidth]{figures/angle}
  \caption{Left panel: distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136. VFTS682 is not an outlier, but
    its relative proper motion matches the expected value if it were indeed
    ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. The top axis shows the conversion to physical units
    assuming a distance of 50\,kpc. Right panel:  distribution of
    angles between the relative proper motion direction and the radial
    direction to the star. The error bars from \emph{Gaia} for VFTS682 are large, but
    the best value is in agreement with the hypothesis of dynamical
    ejection. In both
    panels, the dark blue histograms contain 317 
    stars with error smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
    lighter blue histograms contain 36 stars with errors smaller than $0.05\,\mathrm{mas \
      yr^{-1}}$.}
  \label{fig:mu_dist}
\end{figure*}
